\mireval{}

### 2014-05-06 paper/paper.tex
Updating mir_eval formatting

\def\mireval{\texttt{mir\_eval}}

% ------
\title{mir\_eval}

@@

\begin{document}
%
\maketitle
%
\begin{abstract}
Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.  We present mir\_eval, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.  In the present work, we enumerate the metrics implemented by mir\_eval and quantitatively compare each to an existing implementation.  When the score reported by mir\_eval differs substantially from the reference, we detail the differences in implementation.  We also provide a brief overview of mir\_eval's architecture, design, and intended use.
\end{abstract}
%
\section{Evaluating MIR Algorithms}

@@

Motivated by these criteria, we present \mireval, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
The present work first discusses the architecture and design of \mireval in Section \ref{sec:architecture}.
In Section \ref{sec:tasks}, we describe all of the tasks covered by \mireval and the metrics included.
In order to validate our implementation decisions, we compare \mireval to existing software in Section \ref{sec:comparison}.
Finally, we discuss and summarize our contributions in Section \ref{sec:discussion}.

\section{mir\_eval's architecture}
\label{sec:architecture}

@@

\section{Tasks included in mir\_eval}
\label{sec:tasks}

@@

mir\_eval includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.

@@

\mireval implements the following MIREX-compatible boundary detection metrics:
\begin{description}
\item[Boundary detection:] precision, recall, and F-measure for detecting boundary
events within a tolerance window $w\in \{0.5, 3\}$~\cite{turnbull2007supervised};
\item[Boundary deviation:] median absolute time difference from a reference boundary
to its nearest estimated boundary, and vice versa~\cite{turnbull2007supervised},
\end{description}
and the following structure annotation metrics
\begin{description}
\item[Pairwise classification:] precision, recall, and F-measure for classifying pairs
of sampled time instants as belonging to the same structural
component~\cite{levy2008structural};
\item[Rand index:\footnote{The MIREX results page refers to Rand index as ``random
clustering index''.}] reference and estimated annotations are sampled uniformly
throughout the track, and the induced clusterings are compared by the Rand index
~\cite{rand1971objective};
\item[Normalized conditional entropy:] reference and estimated labels are sampled
uniformly, and interpreted as samples of random variables $Y_R, Y_E$, which are
computed by estimating the conditional entropy of $Y_R$ given $Y_E$
(\emph{under-segmentation}) and $Y_E$ given $Y_R$ 
(\emph{over-segmentation})~\cite{lukashevich2008towards}.
\end{description}

@@

For this reason, the melody evaluator in mir\_eval uses $1^{st}$-order (linear)
interpolation by default in order to map the reference and estimate sequences
onto a common time-grid. Assuming the original timestamps of both sequences
correspond to the \textit{center} of each analysis frame (as they should),
using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
returned by mir\_eval are lower-bounded by the MIREX results and are, in our
view, more accurate.

>>>>

\def\mireval{\texttt{mir\char`_eval}}

% ------
\title{\mireval{}}

@@

\begin{document}
%
\maketitle
%
\begin{abstract}
Central to the field of MIR research is the evaluation of algorithms used to extract information from music data.  We present \mireval{}, an open source software library which provides a transparent and easy-to-use implementation of the most common metrics used to measure the performance of MIR algorithms.  In the present work, we enumerate the metrics implemented by \mireval{} and quantitatively compare each to an existing implementation.  When the score reported by \mireval{} differs substantially from the reference, we detail the differences in implementation.  We also provide a brief overview of \mireval{}'s architecture, design, and intended use.
\end{abstract}
%
\section{Evaluating MIR Algorithms}

@@

Motivated by these criteria, we present \mireval{}, a software package which intends to provide an easy and standardized way to evaluate MIR systems.
The present work first discusses the architecture and design of \mireval{} in Section \ref{sec:architecture}.
In Section \ref{sec:tasks}, we describe all of the tasks covered by \mireval{} and the metrics included.
In order to validate our implementation decisions, we compare \mireval{} to existing software in Section \ref{sec:comparison}.
Finally, we discuss and summarize our contributions in Section \ref{sec:discussion}.

\section{\mireval{}'s architecture}
\label{sec:architecture}

@@

\section{Tasks included in \mireval{}}
\label{sec:tasks}

@@

\mireval{} includes the following metrics for beat tracking, which are defined in detail in \cite{davies2009evaluation}: The \textbf{F-measure} of the beat sequence, where an estimated beat is considered correct if it is sufficiently close to a reference beat; \textbf{Cemgil's score}, which computes the sum of Gaussian errors for each beat; \textbf{Goto's score}, a binary score which is 1 when some specific heuristic criteria are met, \textbf{McKinney's P-score}, which computes the cross-correlation of the estimated and reference beat sequences represented as impulse trains; \textbf{continuity-based scores} which compute the proportion of the beat sequence which is continuously correct; and finally the \textbf{information gain} of the beat error histogram to a uniform distribution.

@@

\mireval{} implements the following MIREX-compatible boundary detection metrics:
\begin{description}
\item[Boundary detection:] precision, recall, and F-measure for detecting boundary
events within a tolerance window $w\in \{0.5, 3\}$~\cite{turnbull2007supervised};
\item[Boundary deviation:] median absolute time difference from a reference boundary
to its nearest estimated boundary, and vice versa~\cite{turnbull2007supervised},
\end{description}
and the following structure annotation metrics
\begin{description}
\item[Pairwise classification:] precision, recall, and F-measure for classifying pairs
of sampled time instants as belonging to the same structural
component~\cite{levy2008structural};
\item[Rand index:\footnote{The MIREX results page refers to Rand index as ``random
clustering index''.}] reference and estimated annotations are sampled uniformly
throughout the track, and the induced clusterings are compared by the Rand index
~\cite{rand1971objective};
\item[Normalized conditional entropy:] reference and estimated labels are sampled
uniformly, and interpreted as samples of random variables $Y_R, Y_E$, which are
computed by estimating the conditional entropy of $Y_R$ given $Y_E$
(\emph{under-segmentation}) and $Y_E$ given $Y_R$ 
(\emph{over-segmentation})~\cite{lukashevich2008towards}.
\end{description}

@@

For this reason, the melody evaluator in \mireval{} uses $1^{st}$-order (linear)
interpolation by default in order to map the reference and estimate sequences
onto a common time-grid. Assuming the original timestamps of both sequences
correspond to the \textit{center} of each analysis frame (as they should),
using $1^{st}$-order rather than $0^{th}$-order interpolation means the results
returned by \mireval{} are lower-bounded by the MIREX results and are, in our
view, more accurate.
